Bayesian Sparsification of $\cplx$-valued networks

### 2019-11-08 paper/paper.tex
merged c-gauss and local rep trick subsections

Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
of $\cplx$-argument, \cite{adali_complex-valued_2011}. The rules it defines satisfy intuitive
linearity, product and chain rules, and respect complex conjugation, but most importantly the
$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
as a basis for $\cplx$ version of backpropagation in \cite{benvenuto_complex_1992} and
\cite{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).

\todo{read on holomorphic nets}

@@

%notation
We first clarify some notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate. By $e_i$
we denote the $i$-th real unit vector of dimensionality \textbf{conforming} to the matrix-vector
expression it is used in. $\vec{M}$ denotes row-major flattening of $M$ into a vector, i.e.
in lexicographic order of its indices. $\otimes$ denotes the Kronecker product, for which we
note the following identities $
  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
$, and $
  (P \otimes R) (C \otimes S) = P Q \otimes R S
$, \cite{petersen_matrix_2012}.
% It follows from the definition of the Kronecker product
% of $P$ and $R^\top$ and the row-major order vectorization.
Finally, $
  \diag{}
    \colon \mathbb{K}^n \to \mathbb{K}^{n\times n}
    \colon v \mapsto (\delta_{ij} v_i)_{ij}
$ is a diagonal matrix embedding, $\mathbb{K} = \real$ or $\cplx$.

\subsection{$\cplx$-Gaussian Variational Approximation} % (fold)
\label{sub:c_gaussian_variational_approximation}

@@

% subsection c_gaussian_variational_approximation (end)

\subsection{Local reparameterization trick} % (fold)
\label{sub:local_reparameterization_trick}

@@

\eqref{eq:cplx-gauss-trick} essentially requires three matrix-vector operations: $\mu x + b$,
$\Sigma \lvert x \rvert^2$ and $C x^2$ with the modulus and power applied elementwise. Similar
to $\real$ case, variational dropout for $\cplx$ convolutions draws independent kernel $W$
for each spatial patch in the input, since a convolution is a matrix product of $W$, unrolled
into a toeplitz matrix, and flattened intput $\vec{x}$. Weight sharing is essentially pushed
to shared variational parameters $\theta$ in the approximation $q_\theta$. The rationale
is to reduce correlation in the gradient estimator stemming from kernel weights being
shared between overlapping patches, \cite{kingma_variational_2015,citation_needed}. Thus
\eqref{eq:cplx-gauss-trick} requires computing $\cplx$ convolutions of $x$, complex square
$x^2$, and amplitude $\lvert x \rvert^2$ with the mean, relation, and variance kernels,
respectively.

% subsection local_reparameterization_trick (end)

>>>>

Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
of $\cplx$-argument, \cite{adali_complex-valued_2011}. The rules it defines satisfy intuitive
linearity, product and chain rules, and respect complex conjugation, but most importantly the
$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
as a basis for $\cplx$ version of backpropagation in \cite{benvenuto_complex_1992} and
\cite{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
%
\todo{read on holomorphic nets}

@@

%notation
We first clarify some notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate. By $e_i$ we
denote the $i$-th real unit vector of dimensionality \textit{conforming} to the matrix-vector
expression it is used in. $\vec{M}$ denotes \textit{row-major} flattening of $M$ into a vector,
i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds $\cplx^n$ into $n\times n$
diagonal matrices. $\otimes$ denotes the Kronecker product, for which we note the following
identities $
  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
$, and $
  (P \otimes R) (C \otimes S) = P Q \otimes R S
$, \cite{petersen_matrix_2012}.
% It follows from the definition of the Kronecker product
% of $P$ and $R^\top$ and the row-major order vectorization.

\subsection{Complex Gaussians and Local Reparameterization} % (fold)
\label{sub:c_gauss_and_local_rep}

@@

@@

\eqref{eq:cplx-gauss-trick} essentially requires three matrix-vector operations: $\mu x + b$,
$\Sigma \lvert x \rvert^2$ and $C x^2$ with the modulus and power applied elementwise. Similar
to $\real$ case, variational dropout for $\cplx$ convolutions draws independent kernel $W$
for each spatial patch in the input, since a convolution is a matrix product of $W$, unrolled
into a toeplitz matrix, and flattened intput $\vec{x}$. Weight sharing is essentially pushed
to shared variational parameters $\theta$ in the approximation $q_\theta$. The rationale
is to reduce correlation in the gradient estimator stemming from kernel weights being
shared between overlapping patches, \cite{kingma_variational_2015,citation_needed}. Thus
\eqref{eq:cplx-gauss-trick} requires computing $\cplx$ convolutions of $x$, complex square
$x^2$, and amplitude $\lvert x \rvert^2$ with the mean, relation, and variance kernels,
respectively.
%
\todo{other reasons for patch-independent weights}

% subsection c_gauss_and_local_rep (end)
